From Freebase to Wikidata: The Great Migration

### 2015-10-05 paper.tex
Reworked Freebase subsection.

Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open source and
collaborative knowledge base created in 2007 by Metaweb and bought in 2010 by Google.
It was used as the open core of the Google Knowledge Graph,
and also in many use cases outside of Google.
Due to the success of Wikidata,
it was decided to close Freebase and support the migration of Freebase' content to Wikidata.
Freebase' content relies on the notions of topics, facts, types, and properties.
Each Freebase topic has a~stable identifier called a~mid and one or more types
and uses properties from these types in order to provide facts.
For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
and the type \texttt{/government/us\_president} that allows the entity to have
a fact with the property \texttt{/government/us\_president/presidency\_number}
and the literal integer ``44'' as the value.

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/freebase-cvt-obama.png}
\caption{Example of CVT: presidency of Barack Obama}
\label{fig-cvt-obama}
\end{figure}

To represent complex values like geocoordinates or to annotate relations,
for example in order to add start and end dates for a~position held,
Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig-cvt-obama}).
They behave like topics, \emph{e.g.}, have a~mid and can have types,
but do not have the \texttt{/common/topic} type.
The content of Freebase has been imported from various sources like Wikipedia or IMDB
and, so, Google does not own the copyright of some parts of the Freebase content
like images or long entity descriptions extracted from Wikipedia.
As of the closing of Freebase, it counted more than 3~billion facts
about almost 50M~entities.

@@

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/Wikidata-statement.png}
\caption{An example of Wikidata statement (from
\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
\label{fig-statement}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/primary-sources.png}
\caption{Primary Sources user interface}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/facts-topics-mapping.png}
\caption{Number of mapped and not mapped topics with more than x facts.
Note the log scale on both axis.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/wikidata-statement-obama.png}
\caption{Target Wikidata statement}
\label{fig-statement-obama}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/wikidata-time-space.png}
\caption{Time and spatial distribution of Wikidata items.
Longitude is in $x$ axis and time, following a~power law ($y' = y^8$), is in $y$ axis}
\label{fig-time-space-wikidata}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8.45 cm]{img/freebase-time-space.png}
\caption{Same figure for Freebase entities}
\label{fig-time-space-freebase}
\end{figure}

>>>>

Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open source and
collaborative knowledge base created in 2007 by Metaweb and acquired in 2010 by Google.
It was used as the open core of the Google Knowledge Graph,
and also has many use cases outside of Google.

Due to the success of Wikidata,
it was decided to close Freebase and support the migration of its contents to Wikidata.
Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
Each Freebase topic has a~stable identifier called \emph{``mid''} (for Metaweb ID),
one or more types, and uses properties from these types in order to provide facts.
For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
and the type \texttt{/government/us\_president} that allows the entity to have
a fact with the property \texttt{/government/us\_president/presidency\_number}
and the literal integer ``44'' as the value.

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/freebase-cvt-obama.png}
\caption{\todo{Crop, get PDF version} Example of CVT: presidency of Barack Obama}
\label{fig-cvt-obama}
\end{figure}

To represent complex values like geographic coordinates or to annotate relations,
for example, in order to add start and end dates for a~position held,
Freebase has introduced the notion of Compound Value Types (CVTs, see \autoref{fig-cvt-obama}).
They behave like topics, \emph{e.g.}, have a~mid and can have types,
but do not have the \texttt{/common/topic} type.

The contents of Freebase have been imported from various sources like Wikipedia
or the Internet Movie Database IMDB,
in consequence Google does not own the copyright of some parts of the contents of the knowledge base
like images or long entity descriptions extracted from Wikipedia.
As of the closing of Freebase on March~31, 2015,
it counted more than 3~billion facts about almost 50M~entities.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/Wikidata-statement.png}
\caption{\todo{Get PDF version} An example of Wikidata statement (from
	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
\label{fig-statement}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/primary-sources.png}
\caption{Primary Sources user interface}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/facts-topics-mapping.png}
\caption{Number of mapped and not mapped topics with more than x facts.
Note the log scale on both axis.}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/wikidata-statement-obama.png}
\caption{Target Wikidata statement}
\label{fig-statement-obama}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/wikidata-time-space.png}
\caption{Time and spatial distribution of Wikidata items.
Longitude is in $x$ axis and time, following a~power law ($y' = y^8$), is in $y$ axis}
\label{fig-time-space-wikidata}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/freebase-time-space.png}
\caption{Same figure for Freebase entities}
\label{fig-time-space-freebase}
\end{figure}
